---
title: "final case_with drg flipped"
author: "Saravind"
date: "2023-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data <- read.csv("OUData.csv")
```

```{r}
data[data=="NULL"] <-NA
colSums(is.na(data))
```
```{r}
data <- na.omit(data)
```

```{r}
colSums(is.na(data))
```

```{r}
data$ObservationRecordKey <- NULL
data$InitPatientClassAndFirstPostOUClass <- NULL
```

```{r}
summary(data)
```
```{r}
data$Gender<-as.factor(data$Gender)
data$PrimaryInsuranceCategory<- as.factor(data$PrimaryInsuranceCategory)
data$DRG01<- as.factor(data$DRG01)

```

```{r}
data$BloodPressureUpper<- as.numeric(data$BloodPressureUpper)
data$BloodPressureDiff<- as.numeric(data$BloodPressureDiff)
data$Pulse <- as.numeric(data$Pulse)
data$PulseOximetry <- as.numeric(data$PulseOximetry)
data$Respirations <- as.numeric(data$Respirations)
data$Temperature <- as.numeric(data$Temperature)

```
```{r}
data <- na.omit(data)
```


```{r}
colSums(is.na(data))
```



```{r}
summary(data)
```

```{r}

# Spliting data
set.seed(123)
train_idx <- sample(nrow(data), round(0.7*nrow(data)),replace = FALSE)
train_data <- data[train_idx, ]
test_data <- data[-train_idx, ]

# Fitting logistic regression model
model <- glm(Flipped ~ ., data = train_data, family = "binomial")

# Predicting probability of flipped DRG code for test set
pred_probs <- predict(model, newdata = test_data, type = "response")


test_data$pred_probs <- pred_probs
drg_probs <- aggregate(pred_probs ~ DRG01, data = test_data, FUN = mean)
drg_probs <- drg_probs[order(drg_probs$pred_probs, decreasing = TRUE), ]

```



```{r}
library(dplyr)

# Combined predicted probabilities with DRG codes
pred_data <- test_data %>%
  select(DRG01, Flipped) %>%
  mutate(pred_probs = pred_probs)

# Grouped by DRG code and calculated mean predicted probability of being flipped
pred_summary <- pred_data %>%
  group_by(DRG01) %>%
  summarize(mean_pred_prob = mean(pred_probs), total_flipped = sum(Flipped), n = n()) %>%
  filter(n >= 10) %>%
  arrange(desc(mean_pred_prob))

#DRG codes with highest mean predicted probabilities of being flipped
head(pred_summary, n = 10)

```
#for DRG code 558, there were 11 patients with that DRG code in the test set, and out of those 11 patients, 6 were predicted to have a flipped DRG code with a mean predicted probability of 0.824. Similarly, for DRG code 428, there were 11 patients with that DRG code in the test set, and out of those 11 patients, 7 were predicted to have a flipped DRG code with a mean predicted probability of 0.649.

#The "n" column shows the total number of patients in the test set with each DRG code, regardless of whether they had a flipped DRG code or not.













